# Practice Problems

## R Project Redone

```{r}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
library(tidyverse)
data <- read.csv(file = "~/Downloads/project_data_file.csv")
print(data)
```

### 1 and 2

Create a new column called Birth_Month which has only the month portion of Birth_Month_Year. Create a new column called Birth_Year which has only the year portion of Birth_Month_Year.

```{r}
data_alt <- data %>%
  separate_wider_delim(Birth_Month_Year, delim=",", names = c("Birth_Month", "Birth_Year"))

print(data_alt)
```

### 3 and 4

Since the birth month and birth year were open ended fields, there are many inconsistencies in the data. Standardize the values for Birth_Month and Birth_Year. Show the five most frequent birth months, and the five least frequent birth months.

```{r}
data_alt2 <- data_alt %>%
  
  mutate(Birth_Month = case_when(
    Birth_Month == "7" ~ "July",
    Birth_Month == "11" ~ "November",
    Birth_Month == "9" ~ "September",
    .default = Birth_Month)) %>%
  
  mutate(Birth_Month = str_to_title(str_trim(Birth_Month))) %>%
  
  mutate(Birth_Year = as.numeric(str_trim(Birth_Year)))

print(data_alt2)
```

```{r}
data_alt2 %>% count(Birth_Month, sort = TRUE) %>% head(5)
data_alt2 %>% count(Birth_Month, sort = TRUE) %>% tail(5)

data_alt2 %>% count(Birth_Year, sort = TRUE) %>% head(5)
data_alt2 %>% count(Birth_Year, sort = TRUE) %>% tail(5)
```

### 6 and 7

```{r}
data_alt3 <- data_alt2 %>%
  mutate(State = ifelse(State %in% state.name,State,NA))

print(data_alt3)
```

### 9

```{r}
data_alt4 <- data_alt3 %>%
  rowwise() %>%
  mutate(How_Hear_About_Program = substring(How_Hear_About_Program, 4, nchar(How_Hear_About_Program))) %>%
           ungroup()

print(data_alt4)
```

### 
